---
title: "estimations"
author: "Liz P. Noguera Z."
orcid: "https://orcid.org/0000-0001-5057-8458"
output: html_document
#output: github_docu@ment

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains ALE and zDALYs estimations based on the findings of the systematic review

Importing helper functions
```{r, include=FALSE}
sys.source("helper.R", envir = knitr::knit_global())
```

Importing data
```{r}
sys.source("data_shared.R", envir = knitr::knit_global())

n = 100000 #number of iterations

set.seed(1000)
 ```

Packages

```{r}
#library("fitdistrplus")
#library(confintr)
```
 1. Rabies, Africa and Asia. DOI: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2626230/pdf/15976877.pdf
```{r}
#### DALY estimation total
daly_rabies_africa_asia <- runif(n, min = rabies_africa_asia$daly_total[1],
                                 max = rabies_africa_asia$daly_total[2])
quantile(daly_rabies_africa_asia, c(0.05,0.5,0.95))

#### DALY estimation total without post-exposure treatment
daly_rabies_africa_asia_no_tx <- runif(n, min = rabies_africa_asia$daly_no_tx[1],
                                       max = rabies_africa_asia$daly_no_tx[2])
quantile(daly_rabies_africa_asia_no_tx, c(0.05,0.5,0.95))

#### DALY estimation Africa
daly_rabies_africa <- runif(n, min = rabies_africa_asia$daly_africa[1],
                            max = rabies_africa_asia$daly_africa[2])
quantile(daly_rabies_africa , c(0.05,0.5,0.95))

#### DALY estimation Asia
daly_rabies_asia <- runif(n, min = rabies_africa_asia$daly_asia[1],
                          max = rabies_africa_asia$daly_asia[2])
quantile(daly_rabies_asia , c(0.05,0.5,0.95))

##### ALE estimation total
ale_rabies_africa_asia_total <- rabies_africa_asia$livestock_loss/rabies_africa_asia$gni_total       
quantile(ale_rabies_africa_asia_total, c(0.05,0.5,0.95))

##### ALE estimation Africa
ale_rabies_africa <- rabies_africa_asia$livestock_loss_africa/rabies_africa_asia$gni_africa    
quantile(ale_rabies_africa, c(0.05,0.5,0.95))

##### ALE estimation Asia
ale_rabies_asia <- rabies_africa_asia$livestock_loss_asia/rabies_africa_asia$gni_asia   
quantile(ale_rabies_asia, c(0.05,0.5,0.95))


##### zDALY estimation total
zdaly_rabies_africa_asia <- daly_rabies_africa_asia + ale_rabies_africa_asia_total    
quantile(zdaly_rabies_africa_asia, c(0.05,0.5,0.95))

brucellosis_kz_daly <- rpois(n, kazakhstan_brucellosis$daly)
quantile(brucellosis_kz_daly, c(0.025,0.5,0.975))

##### zDALY estimation total without post-exposure treatment
zdaly_rabies_africa_asia_no_tx <- daly_rabies_africa_asia_no_tx + ale_rabies_africa_asia_total    
quantile(zdaly_rabies_africa_asia_no_tx, c(0.05,0.5,0.95))

##### zDALY estimation Africa
zdaly_rabies_africa <- daly_rabies_africa + ale_rabies_africa
quantile(zdaly_rabies_africa, c(0.05,0.5,0.95))

##### zDALY estimation Asia
zdaly_rabies_asia <- daly_rabies_asia + ale_rabies_asia   
quantile(zdaly_rabies_asia, c(0.05,0.5,0.95))
```

 2. Cystic echinococcosis, Worldwide. DOI: 10.3201/eid1202.050499 
```{r}
##### Creates randomly a sequence between a range
daly_unadj_random <- runif(n, min = world_CE$daly_unadjusted[1],
                           max = world_CE$daly_unadjusted[2])
quantile(daly_unadj_random, c(0.025,0.5,0.975))

daly_adj_random <- runif(n, min = world_CE$daly_adjusted[1],
                         max = world_CE$daly_adjusted[2])
quantile(daly_adj_random, c(0.025,0.5,0.975))

animal_loss_unadj_random <- runif(n, min = world_CE$animal_loss_unadjusted[1],
                                  max = world_CE$animal_loss_unadjusted[2])

animal_loss_adj_random <- runif(n, min = world_CE$animal_loss_adjusted[1],
                                max = world_CE$animal_loss_adjusted[2])

##### ALE estimation

world_CE_ale_unadj <- animal_loss_unadj_random / mozambique$gni        ###### unadjusted ALE
quantile(world_CE_ale_unadj , c(0.025,0.5,0.975))


world_CE_ale_adj <- animal_loss_adj_random / mozambique$gni           ###### adjusted ALE
quantile(world_CE_ale_adj , c(0.025,0.5,0.975))

##### zDALY estimation
world_CE_zdaly_unadj <- daly_unadj_random + world_CE_ale_unadj        ###### unadjusted zDALY
quantile(world_CE_zdaly_unadj, c(0.025,0.5,0.975))

world_CE_zdaly_adj <- daly_adj_random + world_CE_ale_adj              ###### adjusted zDALY
quantile(world_CE_zdaly_adj, c(0.025,0.5,0.975))
```


 3. Echinococcosis, Shiqu County, China. DOI: https://doi.org/10.4269/ajtmh.2005.73.2
```{r}
##### Creates randomly a sequence between a range
animal_loss_random1 <- runif(n, min = china_CE$animal_loss_1[1], max = china_CE$animal_loss_1[2])

#animal_loss_random1 <- rgamma(n, mean= 278292)
animal_loss_random2 <- runif(n, min = china_CE$animal_loss_2[1], max = china_CE$animal_loss_2[2])


##### ALE estimation
china_CE_ale1 <- animal_loss_random1 / china_CE$gni           
quantile(china_CE_ale1, c(0.025,0.5,0.975))

china_CE_ale2 <- animal_loss_random2 / china_CE$gni           
quantile(china_CE_ale2, c(0.025,0.5,0.975))

##### zDALY estimation
china_CE_zdaly1 <- china_CE$daly + china_CE_ale1     
quantile(china_CE_zdaly1, c(0.025,0.5,0.975))

china_CE_zdaly2 <- china_CE$daly + china_CE_ale2      
quantile(china_CE_zdaly2, c(0.025,0.5,0.975))
```

 4. Cysticercosis (Taenia solium), Mozambique. DOI: https://doi.org/10.1186/s12879-018-3030-z
```{r, warning=FALSE}
##### Fitting gamma distribution
gamma_paramater_daly <- fit_gamma(mozambique$daly[1], mozambique$daly[2])$par
gamma_parameter_num_infected <- fit_gamma(mozambique$num_infected[1], mozambique$num_infected[2])$par 
gamma_parameter_animal_value <- fit_gamma(mozambique$animal_value[1], mozambique$animal_value[2])$par 


total_infected <- rgamma(n, gamma_parameter_num_infected[1], gamma_parameter_num_infected[2])
animal_value_total <- rgamma(n, gamma_parameter_animal_value[1], gamma_parameter_animal_value[2])

##### Estimating animal loss
mozambique_total_animal_loss <- total_infected * animal_value_total * mozambique$reduced_value * mozambique$sold

mozambique_total_animal_loss1 <- total_infected * animal_value_total * mozambique$reduced_value 
quantile(mozambique_total_animal_loss1, c(0.025,0.5,0.975))

## DALY estimation
mozambique_daly <- rgamma(n, gamma_paramater_daly[1], gamma_paramater_daly[2])
quantile(mozambique_daly, c(0.025,0.5,0.975))

## ALE estimation
mozambique_ale <- mozambique_total_animal_loss / mozambique$gni
quantile(mozambique_ale , c(0.025,0.5,0.975))

## ALE without the proportion of pigs sold
mozambique_ale1 <- mozambique_total_animal_loss1 / mozambique$gni
quantile(mozambique_ale1 , c(0.025,0.5,0.975))

## zDALY estimation
mozambique_zdaly <- mozambique_ale + mozambique_daly
quantile(mozambique_zdaly, c(0.025,0.5,0.975))


## zDALY without the proportion of pigs sold
mozambique_zdaly1 <- mozambique_ale1 + mozambique_daly
quantile(mozambique_zdaly1, c(0.025,0.5,0.975))
```

 5. Cysticercosis (Taenia solium), Cameroon. DOI: https://doi.org/10.1371/journal.pntd.0000406
```{r}
##### Creates randomly a sequence between a range
animal_loss <- runif(n, min = cameroon$animal_loss[1], max = cameroon$animal_loss[2])

##### DALY estimation
cameroon_daly <- runif(n, min = cameroon$daly[1], max = cameroon$daly[2])
quantile(cameroon_daly, c(0.025,0.5,0.975))

##### ALE estimation
cameroon_ALE <- animal_loss/ cameroon$gni           
quantile(cameroon_ALE, c(0.025,0.5,0.975))

##### zDALY estimation
cameroon_zdaly <- cameroon_daly + cameroon_ALE     
quantile(cameroon_zdaly, c(0.025,0.5,0.975))
```

 6. Cystic echinococcosis, Peru. DOI: https://doi.org/10.1371/journal.pntd.0001179
```{r}
##### Creates randomly a sequence between a range
peru_animal_loss <- runif(n, min = peru$animal_loss[1], max = peru$animal_loss[2])

##### ALE estimation
peru_ALE <- peru_animal_loss/ peru$gni           
quantile(peru_ALE, c(0.025,0.5,0.975))

##### zDALY estimation
peru_zdaly <- peru$daly_total + peru_ALE    
quantile(peru_zdaly, c(0.025,0.5,0.975))
```

 7. Rabies, Worldwide. DOI: https://doi.org/10.1371/journal.pntd.0003709
```{r}

#### Select min and max of two columns for each row to simulate an uniform distribution
f <- Vectorize(function(x,y) runif(n,min=x,max=y),vectorize.args = c("x","y"))

 asia2_ale  <- with(asia2,f(livestock_loss_lower,livestock_loss_upper)) / mean(asia2$gni_2010)
 quantile(asia2_ale, c(0.025,0.5,0.975))
 
 asia3_ale  <- with(asia3,f(livestock_loss_lower,livestock_loss_upper)) / mean(asia3$gni_2010)
 quantile(asia3_ale, c(0.025,0.5,0.975))
 
 asia4_ale  <- with(asia4,f(livestock_loss_lower,livestock_loss_upper)) / mean(asia4$gni_2010)
 quantile(asia4_ale, c(0.025,0.5,0.975))
 
 china_ale  <- with(china,f(livestock_loss_lower,livestock_loss_upper)) / mean(china$gni_2010)
 quantile(china_ale, c(0.025,0.5,0.975))
 
 india_ale  <- with(india,f(livestock_loss_lower,livestock_loss_upper)) / mean(india$gni_2010)
 quantile(india_ale, c(0.025,0.5,0.975))
 
 indonesia_ale  <- with(indonesia,f(livestock_loss_lower,livestock_loss_upper)) / mean(indonesia$gni_2010)
 quantile(indonesia_ale, c(0.025,0.5,0.975))
 
 north_africa_ale  <- with(north_africa,f(livestock_loss_lower,
                                          livestock_loss_upper)) / mean(north_africa$gni_2010)
 quantile(north_africa_ale, c(0.025,0.5,0.975))
 
 congo_basin_ale  <- with(congo_basin,f(livestock_loss_lower,
                                        livestock_loss_upper)) / mean(congo_basin$gni_2010)
 quantile(congo_basin_ale, c(0.025,0.5,0.975))
 
 west_africa_ale  <- with(west_africa,f(livestock_loss_lower,
                                        livestock_loss_upper)) / mean(west_africa$gni_2010)
 quantile(west_africa_ale, c(0.025,0.5,0.975))
 
 sadc_ale  <- with(sadc,f(livestock_loss_lower,
                          livestock_loss_upper)) / mean(sadc$gni_2010)
 quantile(sadc_ale, c(0.025,0.5,0.975))
 
 andean_ale  <- with(andean,f(livestock_loss_lower,
                              livestock_loss_upper)) / mean(andean$gni_2010)
 quantile(andean_ale , c(0.025,0.5,0.975))
 
 brazil_ale  <- with(brazil,f(livestock_loss_lower,
                              livestock_loss_upper)) / mean(brazil$gni_2010)
 quantile(brazil_ale , c(0.025,0.5,0.975))
 
 caribbean_ale  <- with(caribbean,f(livestock_loss_lower,
                                    livestock_loss_upper)) / mean(caribbean$gni_2010)
 quantile(caribbean_ale, c(0.025,0.5,0.975))

 central_ale  <- with(central,f(livestock_loss_lower,
                                livestock_loss_upper)) / mean(central$gni_2010)
 quantile(central_ale, c(0.025,0.5,0.975))
 
 southern_cone_ale  <- with(southern_cone,f(livestock_loss_lower,
                                            livestock_loss_upper)) / mean(southern_cone$gni_2010)
 quantile(southern_cone_ale, c(0.025,0.5,0.975))
 
 eastern_europe_ale  <- with(eastern_europe,f(livestock_loss_lower,
                                              livestock_loss_upper)) / mean(eastern_europe$gni_2010)
 quantile(eastern_europe_ale, c(0.025,0.5,0.975))
 
 eurasia_ale  <- with(eurasia,f(livestock_loss_lower,
                                livestock_loss_upper)) / mean(eurasia$gni_2010)
 quantile(eurasia_ale, c(0.025,0.5,0.975))
 
 
 middle_east_ale <- with(middle_east,f(livestock_loss_lower,
                                       livestock_loss_upper)) / mean(middle_east$gni_2010)
 quantile( middle_east_ale, c(0.025,0.5,0.975)
           
           
#### Total ALE: With the data of the study
 
 total_ale_rabies_world1 <- world_rabies$animal_loss / mean(world_rabies_data$gni_2010) 
 quantile(total_ale_rabies_world1, c(0.025,0.5,0.975))
 

 #### Total ALE: based on our simulates
  total_ale_rabies_world2 <- rpois (n, c(asia2_ale,asia3_ale, asia4_ale, china_ale, india_ale,
                                   indonesia_ale, north_africa_ale, congo_basin_ale,
                                   west_africa_ale, sadc_ale, andean_ale, brazil_ale,caribbean_ale,
                                   central_ale,  southern_cone_ale, eastern_europe_ale, eurasia_ale,
                                   middle_east_ale))   #try with the results above
  quantile(total_ale_rabies_world2, c(0.025,0.5,0.975))
  
  
 ######################### 
 #### zDALY = DALY + ALE
 
asia2_zdaly <-  runif(n, min = 80000 , max = 655000) + asia2_ale
quantile(asia2_zdaly, c(0.025,0.5,0.975))


asia3_zdaly <-  runif(n, min = 75000 , max = 853000) + asia3_ale
quantile(asia3_zdaly, c(0.025,0.5,0.975))


asia4_zdaly <-  runif(n, min = 10000 , max = 83000) + asia4_ale
quantile(asia4_zdaly, c(0.025,0.5,0.975))


china_zdaly <-  runif(n, min = 60000, max = 674000) + china_ale
quantile(china_zdaly, c(0.025,0.5,0.975))


india_zdaly <- runif(n, min = 377000, max = 3436000) + india_ale
quantile(india_zdaly, c(0.025,0.5,0.975))
 
 
indonesia_zdaly <- runif(n, min = 12000, max = 198000) + indonesia_ale
quantile(indonesia_zdaly, c(0.025,0.5,0.975))
 

 north_africa_zdaly <- runif(n, min = 38000, max = 467000) + north_africa_ale
 quantile(north_africa_zdaly, c(0.025,0.5,0.975))
 
 
 congo_basin_zdaly <- runif(n, min = 244000,
                            max = 1031000) + congo_basin_ale 
 quantile(congo_basin_zdaly, c(0.025,0.5,0.975))

 
 west_africa_zdaly <- runif(n, min = 206000,
                            max = 971000) + west_africa_ale 
 quantile(west_africa_zdaly , c(0.025,0.5,0.975))
 

 sadc_zdaly  <- runif(n, min = 157000, max = 1713000) + sadc_ale 
 quantile(sadc_zdaly , c(0.025,0.5,0.975))
 
 andean_zdaly  <- runif(n, min = 0, max = 4000) + andean_ale 
 quantile(andean_zdaly , c(0.025,0.5,0.975))
 
 brazil_zdaly  <- runif(n, min = 0, max = 2000) +  brazil_ale  
 quantile(brazil_zdaly, c(0.025,0.5,0.975))
 
 caribbean_zdaly  <- runif(n, min = 4000, max = 17000) +  caribbean_ale 
 quantile(caribbean_zdaly, c(0.025,0.5,0.975))
 
 central_zdaly  <- runif(n, min =0, max = 3000) +  central_ale 
 quantile(central_zdaly, c(0.025,0.5,0.975))
 
 southern_cone_zdaly  <- runif(n, min =0, max = 1000) +  southern_cone_ale 
 quantile(southern_cone_zdaly, c(0.025,0.5,0.975))

 eastern_europe_zdaly  <- runif(n, min =0, max = 5000) +  eastern_europe_ale
 quantile(eastern_europe_zdaly, c(0.025,0.5,0.975))

 eurasia_zdaly  <- runif(n, min =46000, max = 368000) +  eurasia_ale 
 quantile(eurasia_zdaly, c(0.025,0.5,0.975))

 middle_east_zdaly <-  runif(n, min =6000, max = 39000) + middle_east_ale 
 quantile(middle_east_zdaly, c(0.025,0.5,0.975))
 
 
 zdaly_total_rabies_world1 <- runif(n, min = world_rabies$daly[1],
                                    max = world_rabies$daly[2]) + total_ale_rabies_world1
 quantile(zdaly_total_rabies_world1 , c(0.025,0.5,0.975))
 
 zdaly_total_rabies_world2 <- runif(n, min = world_rabies$daly[1],
                                    max = world_rabies$daly[2]) + total_ale_rabies_world2
 quantile(zdaly_total_rabies_world2 , c(0.025,0.5,0.975))
 
```
 
 8. Q fever, Netherlands. DOI: https://doi.org/10.1016/j.prevetmed.2013.06.002
```{r}

#### DALY estimation
netherlands_daly <- runif(n, min = netherlands$daly[1], max = netherlands$daly[2])
quantile(netherlands_daly, c(0.025,0.5,0.975))

netherlands_animal_loss <- netherlands_daly * netherlands$infected_animal

##### ALE estimation
netherlands_ALE <- netherlands_animal_loss/ netherlands$gni          
quantile(netherlands_ALE, c(0.025,0.5,0.975))

##### zDALY estimation
netherlands_zdaly <- netherlands_daly + netherlands_ALE    
quantile(netherlands_zdaly_2007, c(0.025,0.5,0.975))

###### Yearly
netherlands_animal_loss_2007 <- runif(n, min = netherlands$animal_loss[1],
                                      max = netherlands$animal_loss[2]) * 
                                      netherlands$infected_animal_2007

netherlands_animal_loss_2008 <- runif(n, min = netherlands$animal_loss[1],
                                      max = netherlands$animal_loss[2]) * 
                                      netherlands$infected_animal_2008

netherlands_animal_loss_2009 <- runif(n, min = netherlands$animal_loss[1],
                                      max = netherlands$animal_loss[2]) * 
                                      netherlands$infected_animal_2009

netherlands_animal_loss_2010 <- runif(n, min = netherlands$animal_loss[1],
                                      max = netherlands$animal_loss[2]) * 
                                      netherlands$infected_animal_2010

netherlands_animal_loss_2011 <- runif(n, min = netherlands$animal_loss[1],
                                      max = netherlands$animal_loss[2]) * 
                                      netherlands$infected_animal_2011

##### ALE estimation
netherlands_ALE_2007 <- netherlands_animal_loss_2007/ netherlands$gni_2007          
quantile(netherlands_ALE_2007, c(0.025,0.5,0.975))

netherlands_ALE_2008 <- netherlands_animal_loss_2008/ netherlands$gni_2008

netherlands_ALE_2009 <- netherlands_animal_loss_2009/ netherlands$gni_2009   

netherlands_ALE_2010 <- netherlands_animal_loss_2010/ netherlands$gni_2010

netherlands_ALE_2011 <- netherlands_animal_loss_2011/ netherlands$gni_2011

netherlands_ALE_total <- (netherlands_ALE_2007 + netherlands_ALE_2008  +
   netherlands_ALE_2009 + netherlands_ALE_2010 + netherlands_ALE_2011) / 5

##### zDALY estimation
netherlands_zdaly <- runif(n, min = netherlands$daly[1],
                           max = netherlands$daly[2]) + netherlands_ALE_total     #for the period 2007-2011
quantile(netherlands_zdaly, c(0.025,0.5,0.975))

netherlands_zdaly_2007 <- runif(n, min = netherlands$daly[1],
                                max = netherlands$daly[2]) + netherlands_ALE_2007      
quantile(netherlands_zdaly_2007, c(0.025,0.5,0.975))

netherlands_zdaly_2008 <- runif(n, min = netherlands$daly[1], 
                                max = netherlands$daly[2]) + netherlands_ALE_2008      
quantile(netherlands_zdaly_2008, c(0.025,0.5,0.975))

netherlands_zdaly_2009 <- runif(n, min = netherlands$daly[1],
                                max = netherlands$daly[2]) + netherlands_ALE_2009      
quantile(netherlands_zdaly_2009, c(0.025,0.5,0.975))

netherlands_zdaly_2010 <- runif(n, min = netherlands$daly[1],
                                max = netherlands$daly[2]) + netherlands_ALE_2010      
quantile(netherlands_zdaly_2010, c(0.025,0.5,0.975))

netherlands_zdaly_2011 <- runif(n, min = netherlands$daly[1],
                                max = netherlands$daly[2])  + netherlands_ALE_2011      
quantile(netherlands_zdaly_2011, c(0.025,0.5,0.975))
```

 9. Cysticercosis (Taenia solium), Tanzania. DOI: https://doi.org/10.1016/j.actatropica.2015.12.021
```{r, warning=FALSE}
# Fitting gamma distribution
tanzania_gamma_paramater_daly <- fit_gamma(tanzania$daly[1], tanzania$daly[2])$par

tanzania_animal_loss <- runif(n, min = tanzania$pig_loss[1],
                                       max = tanzania$pig_loss[2])

## DALY estimation
tanzania_daly <- rgamma(n, tanzania_gamma_paramater_daly[1], tanzania_gamma_paramater_daly[2])
quantile(tanzania_daly, c(0.025,0.5,0.975))

## ALE estimation
tanzania_ale <- tanzania_animal_loss/ tanzania$gni
quantile(tanzania_ale , c(0.025,0.5,0.975))


## zDALY estimation
tanzania_zdaly <- tanzania_ale + tanzania_daly
quantile(tanzania_zdaly, c(0.025,0.5,0.975))

```

 10. Rabies, Viet Nam. DOI: 10.1371/journal.pntd.0006866
```{r}
##### Creates randomly a sequence between a range for DALY at age of 26
vietnam_daly_26 <- runif(n, min = vietnam$daly_26[10],
                                       max = vietnam$daly_26[3])  # choosing the min and max values over 2005-2014
quantile(vietnam_daly_26, c(0.025,0.5,0.975))                                                              

##### Creates randomly a sequence between a range for DALY at age of 31
vietnam_daly_31 <- runif(n, min = vietnam$daly_31[10],
                                       max = vietnam$daly_31[3])
quantile(vietnam_daly_31, c(0.025,0.5,0.975))

##### Creates randomly a sequence between a range for DALY at age of 36
vietnam_daly_36 <- runif(n, min = vietnam$daly_36[10],
                                       max = vietnam$daly_36[3])
quantile(vietnam_daly_36, c(0.025,0.5,0.975))

## ALE estimation
vietnam_ale <- vietnam$livestock_loss_mean/ mean(vietnam$gni)
quantile(tanzania_ale , c(0.025,0.5,0.975))

## zDALY estimation at age of 26
vietnam_zdaly_26 <- vietnam_ale + vietnam_daly_26
quantile(vietnam_zdaly_26, c(0.025,0.5,0.975))

## zDALY estimation at age of 31
vietnam_zdaly_31 <- vietnam_ale + vietnam_daly_31
quantile(vietnam_zdaly_31, c(0.025,0.5,0.975))

## zDALY estimation at age of 36
vietnam_zdaly_36 <- vietnam_ale + vietnam_daly_36
quantile(vietnam_zdaly_36, c(0.025,0.5,0.975))

## Total zDALY
vietnam_zdaly_total <-  (vietnam_zdaly_26 + vietnam_zdaly_31 + vietnam_zdaly_36)/3
quantile(vietnam_zdaly_total, c(0.025,0.5,0.975))
```
 
 11. Rabies, Kazakhstan. DOI: 10.1371/journal.pntd.0004889
```{r, warning=FALSE}

##### Fitting gamma distribution
gamma_paramater_daly_rabies_kz <- fit_gamma(kz_rabies$daly[1], kz_rabies$daly[2])$par
gamma_paramater_daly_rabies_kz_without_pep <- fit_gamma(kz_rabies$daly_without_PEP[1],
                                                        kz_rabies$daly_without_PEP[2])$par
gamma_paramater_rabies_kz_cattle_loss <- fit_gamma(kz_rabies$cattle_loss[1],
                                                   kz_rabies$cattle_loss[2])$par
gamma_paramater_rabies_kz_sheep_loss <- fit_gamma(kz_rabies$sheep_loss[1],
                                                  kz_rabies$sheep_loss[2])$par
gamma_paramater_rabies_kz_camel_loss <- fit_gamma(kz_rabies$camel_loss[1],
                                                  kz_rabies$camel_loss[2])$par
gamma_paramater_rabies_kz_horse_loss <- fit_gamma(kz_rabies$horse_loss[1],
                                                  kz_rabies$horse_loss[2])$par
gamma_paramater_rabies_kz_total_animal_loss <- fit_gamma(kz_rabies$total_animal_loss[1],
                                                         kz_rabies$total_animal_loss[2])$par

#####  DALY
daly_kz_rabies <-  rgamma(n, gamma_paramater_daly_rabies_kz[1],
                          gamma_paramater_daly_rabies_kz[2])
quantile(daly_kz_rabies, c(0.025,0.5,0.975))

daly_kz_rabies_without_pep <- rgamma(n, gamma_paramater_daly_rabies_kz_without_pep[1],
                                     gamma_paramater_daly_rabies_kz_without_pep[2])
quantile(daly_kz_rabies_without_pep , c(0.025,0.5,0.975))

##### ALE
ale_cattle_kz_rabies <-  rgamma(n, gamma_paramater_rabies_kz_cattle_loss[1],
                                gamma_paramater_rabies_kz_cattle_loss[2]) / kz_rabies$gni_mean
quantile(ale_cattle_kz_rabies, c(0.025,0.5,0.975))

ale_sheep_kz_rabies <-  rgamma(n, gamma_paramater_rabies_kz_sheep_loss[1],
                               gamma_paramater_rabies_kz_sheep_loss[2]) / kz_rabies$gni_mean
quantile(ale_sheep_kz_rabies, c(0.025,0.5,0.975))

ale_camel_kz_rabies <-  rgamma(n, gamma_paramater_rabies_kz_camel_loss[1],
                               gamma_paramater_rabies_kz_camel_loss[2]) / kz_rabies$gni_mean
quantile(ale_camel_kz_rabies, c(0.025,0.5,0.975))

ale_horse_kz_rabies <-  rgamma(n, gamma_paramater_rabies_kz_horse_loss[1],
                               gamma_paramater_rabies_kz_horse_loss[2]) / kz_rabies$gni_mean
quantile(ale_horse_kz_rabies, c(0.025,0.5,0.975))
   
ale_total_kz_rabies <-  rgamma(n, gamma_paramater_rabies_kz_total_animal_loss[1],
                               gamma_paramater_rabies_kz_total_animal_loss[2]) / kz_rabies$gni_mean
quantile(ale_total_kz_rabies, c(0.025,0.5,0.975))   
   
##### zDALY estimation
zdaly_cattle_kz <-  daly_kz_rabies + ale_cattle_kz_rabies
quantile(zdaly_cattle_kz, c(0.025,0.5,0.975)) 

zdaly_sheep_kz <- daly_kz_rabies + ale_sheep_kz_rabies
quantile(zdaly_sheep_kz, c(0.025,0.5,0.975)) 
   
zdaly_camel_kz <- daly_kz_rabies + ale_camel_kz_rabies
quantile(zdaly_camel_kz, c(0.025,0.5,0.975))
   
zdaly_horse_kz <-  daly_kz_rabies + ale_horse_kz_rabies
quantile(zdaly_horse_kz, c(0.025,0.5,0.975))

zdaly_total_kz <-  daly_kz_rabies + ale_total_kz_rabies
quantile(zdaly_total_kz, c(0.025,0.5,0.975))

##### Without PEP
zdaly_cattle_kz_without_pep <-  daly_kz_rabies_without_pep + ale_cattle_kz_rabies
quantile(zdaly_cattle_kz_without_pep, c(0.025,0.5,0.975)) 

zdaly_sheep_kz_without_pep <- daly_kz_rabies_without_pep + ale_sheep_kz_rabies
quantile(zdaly_sheep_kz_without_pep, c(0.025,0.5,0.975)) 
   
zdaly_camel_kz_without_pep <- daly_kz_rabies_without_pep + ale_camel_kz_rabies
quantile(zdaly_camel_kz_without_pep, c(0.025,0.5,0.975))
   
zdaly_horse_kz_without_pep <-  daly_kz_rabies_without_pep + ale_horse_kz_rabies
quantile(zdaly_horse_kz_without_pep, c(0.025,0.5,0.975))

zdaly_total_kz_without_pep <-  daly_kz_rabies_without_pep + ale_total_kz_rabies
quantile(zdaly_total_kz_without_pep, c(0.025,0.5,0.975))
```
 


 12. Brucellosis, Kazakhstan. DOI: 10.1111/zph.12582
```{r}
## Random generations of DALY
brucellosis_kz_daly <- rpois(n, kazakhstan_brucellosis$daly)
quantile(brucellosis_kz_daly, c(0.025,0.5,0.975))

brucellosis_kz_animal_loss <- rpois(n, kazakhstan_brucellosis$livestock_loss)
quantile(brucellosis_kz_animal_loss, c(0.025,0.5,0.975))

## ALE estimation
ale_brucellosis_kz <-  brucellosis_kz_animal_loss / kazakhstan_brucellosis$gni
quantile(ale_brucellosis_kz , c(0.025,0.5,0.975))

## zDALY estimation

zdaly_brucellosis_kz <-  brucellosis_kz_daly + ale_brucellosis_kz
quantile(zdaly_brucellosis_kz, c(0.025,0.5,0.975))
```

13.Leptospirosis, New Zealand. DOI: https://doi.org/10.1111/zph.12668
```{r}
##### ALE
ale_nz <- (nz$beef_cattle_loss + nz$sheep_loss + nz$deer_loss) / nz$gni_mean

##### zDALY
nz_daly <- nz$daly_pop_at_risk + ale_nz 

nz_zdaly_not_risk <- nz$daly_pop_not_at_risk + ale_nz 

nz_daly_total <-  nz$total_daly + ale_nz 

```

 14. Brucella, Anthrax, Tularemia, CCHF, Rabies, Cystic Echinococcosis,
 Toxoplasmosis; Turkey. DOI: 10.33988/auvfd.789598
```{r}
##### Creates randomly a sequence between a range for DALY
###### Brucella

turkey_daly_brucella <- rpois(n,turkey$brucella_daly)
quantile(turkey_daly_brucella, c(0.025,0.5,0.975))

###### Anthrax
turkey_daly_anthrax <- rpois (n,turkey$anthrax_daly)
quantile(turkey_daly_anthrax, c(0.025,0.5,0.975)) 

###### Total DALYs including Brucella, Anthrax, CCHF, Rabies, CE , Toxoplasmosis 
turkey_daly_total <- rpois (n,turkey$total_daly)
quantile(turkey_daly_total, c(0.025,0.5,0.975)) 
   
## ALE estimation
ale_brucella_large_ruminant <- rpois(n, turkey$brucella_large_ruminant_loss) / turkey$gni_mean
quantile(ale_brucella_large_ruminant, c(0.025,0.5,0.975))

ale_brucella_small_ruminant <-  rpois(n, turkey$brucella_small_ruminant_loss) / turkey$gni_mean
quantile(ale_brucella_small_ruminant, c(0.025,0.5,0.975))

ale_brucella_total_animal <- rpois(n, turkey$brucella_total_animal_loss) / turkey$gni_mean
quantile(ale_brucella_total_animal, c(0.025,0.5,0.975)) 

ale_anthrax_large_ruminant <- rpois(n, turkey$anthrax_large_ruminant_loss) / turkey$gni_mean
quantile(ale_anthrax_large_ruminant, c(0.025,0.5,0.975))

ale_anthrax_small_ruminant <- rpois(n, turkey$anthrax_small_ruminant_loss) / turkey$gni_mean
quantile(ale_anthrax_small_ruminant, c(0.025,0.5,0.975))

ale_anthrax_total_animal <- rpois(n, turkey$anthrax_total_animal_loss) / turkey$gni_mean
quantile(ale_anthrax_total_animal, c(0.025,0.5,0.975))

ale_total_turkey <-  rpois(n, turkey$total_animal_loss) / turkey$gni_mean
quantile(ale_total_turkey, c(0.025,0.5,0.975)) 

## zDALY estimation
zdaly_brucella_large_ruminant <- turkey_daly_brucella + ale_brucella_large_ruminant
quantile(zdaly_brucella_large_ruminant, c(0.025,0.5,0.975))  

zdaly_brucella_small_ruminant <- turkey_daly_brucella + ale_brucella_small_ruminant
quantile(zdaly_brucella_small_ruminant, c(0.025,0.5,0.975))  

zdaly_brucella_total_animal <- turkey_daly_brucella + ale_brucella_total_animal
quantile(zdaly_brucella_total_animal, c(0.025,0.5,0.975))  

zdaly_anthrax_large_ruminant <-  turkey_daly_anthrax + ale_anthrax_large_ruminant
quantile(zdaly_anthrax_large_ruminant, c(0.025,0.5,0.975))  

zdaly_anthrax_small_ruminant <- turkey_daly_anthrax + ale_anthrax_small_ruminant
quantile(zdaly_anthrax_small_ruminant, c(0.025,0.5,0.975))

zdaly_anthrax_total_animal <- turkey_daly_anthrax + ale_anthrax_total_animal
quantile(zdaly_anthrax_total_animal, c(0.025,0.5,0.975))  

zdaly_total_turkey <- turkey_daly_total + ale_total_turkey
quantile(zdaly_total_turkey, c(0.025,0.5,0.975))  

```    
